学術論文

### 2024-12-29 articles.Rmd
update

- [49] Matsumoto, K., Hamatani, S., Kunisato, Y., Mizuno, Y. (2024). Components of Cognitive Behavioural Therapy for Mitigating Core Symptoms in Attention-Deficit Hyperactivity Disorder: A Systematic Review and Network Meta-analysis. BMJ Mental Health.

>>>>

- [49] Matsumoto, K., Hamatani, S., Kunisato, Y., Mizuno, Y. (2024). Components of cognitive–behavioural therapy for mitigating core symptoms in attention-deficit hyperactivity disorder: a systematic review and network meta-analys. BMJ Ment Health, 27,e301303. https://mentalhealth.bmj.com/content/27/1/e301303
